---
title: "Homework R in Practice"
author: "Calvin Sibarani, edited by Yurham Afif"
date: "5/17/2021"
output: github_document
---

```{r}
# Install the package if you haven't!
# install.packages('naniar')
library(naniar)
library(tidyverse)
```

```{r}
riskfactors
```
# PACKAGE VISUALISASI
```{r}
#install.packages("visdat")
library(visdat)
```


# PERTANYAAN
Visualize the missing data in riskfactors dataset, with package that we've learned before
Apa yang bisa kita simpulkan dari missing value di data ini? Ide apa yang bisa teman-teman sampaikan untuk mendiagnosa kenapa missing value ini bisa terjadi?

```{r}
# how much is the missing data?
sum(is.na(riskfactors))
# wow

# Summarize missingness in each variable of the `riskfactors` dataset
miss_var_summary(riskfactors)

# Summarize missingness in each case of the `riskfactors` dataset
miss_case_summary(riskfactors)

# visualise missing values
riskfactors %>% 
  vis_miss()
```
```{r}
# try to sort the data by 'age'
# visualise missing values
riskfactors %>% 
  arrange(age) %>% 
  vis_miss()
```
the higher age value, the more missing 'pregnant' data 

```{r}
# try to sort the data by 'income'
# visualise missing values
riskfactors %>% 
  arrange(income) %>% 
  vis_miss()
```
I cant interpret it visually haha

```{r}
# Return the summary of missingness in each variable, 
# grouped by sex, in the `riskfactors` dataset
riskfactors %>% 
  group_by(sex) %>% 
  miss_var_summary()

# Return the summary of missingness in each case, 
# grouped by sex, in the `riskfactors` dataset
riskfactors %>% 
  group_by(sex) %>% 
  miss_case_summary()
```
pregnant data for male are all NA

# Tabulating missingness
```{r}
# Tabulate missingness in each variable and case of the `riskfactors` dataset
miss_var_table(riskfactors)
miss_case_table(riskfactors)

# Tabulate the missingness in each variable, grouped by sex, in the `riskfactors` dataset
riskfactors %>% group_by(sex) %>% miss_var_table()

# Tabulate of missingness in each case, grouped by sex, in the `riskfactors` dataset
riskfactors %>% group_by(sex) %>% miss_case_table()
```

```{r}
# Calculate the summaries for each run of missingness for the variable, health_poor
miss_var_run(riskfactors, var = health_poor)

# Calculate the summaries for each span of missingness, 
# for a span of 4000, for the variable health_poor
miss_var_span(riskfactors, var = health_poor, span_every = 50)

# For each `sex` variable, calculate the run of missingness for health_poor
riskfactors %>% 
  group_by(sex) %>% 
  miss_var_run(var = health_poor)

# For each `month` variable, calculate the span of missingness 
# of a span of 2000, for the variable health_poor
riskfactors %>% 
  group_by(sex) %>% 
  miss_var_span(var = health_poor, span_every = 50)
```
more than half male data for 'health_poor' are incomplete, 
```{r}
# Explore the strange missing values "N/A"
miss_scan_count(data = riskfactors, search = list("N/A"))

# Explore the strange missing values "missing"
miss_scan_count(data = riskfactors, search = list("missing"))

# Explore the strange missing values "na"
miss_scan_count(data = riskfactors, search = list("na"))

# Explore the strange missing values " " (a single space)
miss_scan_count(data = riskfactors, search = list(" "))

# Explore all of the strange missing values, "N/A", "missing", "na", " "
miss_scan_count(data = riskfactors, search = list("N/A", "missing","na", " "))
```
missing values are in a blank data WITHOUT ANY REDUNDANT DATA


```{r}
# investigate weight column
riskfactors %>% 
  mutate(miss_weight = is.na(weight_lbs)) %>% 
  group_by(miss_weight) %>% 
  summarise_all(mean, na.rm=TRUE)
```
missing "weight_lbs" impacts on missing "bmi" data (missing at random)

```{r}
# investigate weight column
riskfactors %>% 
  mutate(miss_pregnant = is.na(pregnant)) %>% 
  group_by(miss_pregnant) %>% 
  summarise_all(mean, na.rm=TRUE)
```
pregnant data is independent from other variable
```{r}
# investigate weight column
riskfactors %>% 
  mutate(miss_healthpoor = is.na(health_poor)) %>% 
  group_by(miss_healthpoor) %>% 
  summarise_all(mean, na.rm=TRUE)
```
missing 'health_poor' data impacts on 'health_physical' and 'health_mental' data with mean equals zero
