---
title: 'Machine Learning: Unsupervised Learning with R'
author: "Adiva Shabana, edited by Yurham Afif"
date: "6/13/2021"
output: github_document
---

# K-means Clustering
Analysis by Yurham Afif

K-means Clustering is an algorithm that groups/cluster data according to the wanted configuration, represented by a centroid which correspond to the mean of points assigned to the clusters.

In this case, we will use dataset `customer_movie_rating.csv` to create a customer segmentation using K-means clustering and determine the best k value.

## Library

Assign the dependence library `tidyverse`, `gridExtra` and `tidyverse`

```{r}
library(tidyverse)  # data manipulation and visualization
library(gridExtra)  # plot arrangement
library(factoextra) # clustering algorithm and visualisation
```

## Read data

This is the code chunk to load `customer_movie_rating.csv`

```{r}
movie_rating <- read_csv('customer_movie_rating.csv')
head(movie_rating)
```

## Data Preparation

check any missing values and standardise the data

```{r}
movie_rating %>% is.na() %>% sum()
rating <- movie_rating %>% scale()
head(rating)
```

```{r}
distance <- get_dist(rating)
fviz_dist(distance)
```


## Computing K-Means

Set the centroid = 2 as we want to group the data into 2 clusters.

```{r}
k2 <- kmeans(rating, centers = 2, nstart = 25)
str(k2)
fviz_cluster(k2, data = rating)
```

What does theis 2 clusters tells us about? Let's try to figure it out by visualise cluster result for each features.

```{r}
rating %>%
  as_tibble() %>%
  mutate(cluster = k2$cluster, # add clustered data into tibble `rating`
        customer = 1:291 ) %>%
  ggplot(aes(Horror, Romcom, color = factor(cluster), label = customer)) +
  geom_text()
```

Cluster 2 rates romance higher than horror, compared to cluster 1 that rates horror higher than romance 

```{r}
rating %>%
  as_tibble() %>%
  mutate(cluster = k2$cluster, # add clustered data into tibble `rating`
        customer = 1:291 ) %>%
  ggplot(aes(Fantasy, Romcom, color = factor(cluster), label = customer)) +
  geom_text()
```

cluster 1 rates romance and fantasy lower than cluster 2 do


## Determining Optimal Clusters

there are three optimal cluster number determination method, i.e. `Elbow Method`, `Average Silhouette Method`, and `Gap Statistics Method`. In this case, we will use `Elbow Method`. The idea is to choose the number which has the most significant difference for the data and not over differentiate it.

```{r}
set.seed(123)
fviz_nbclust(rating, kmeans, method = "wss")
#fviz_nbclust(rating, kmeans, method = "silhouette")
```

From the graph above, we choose k = 3 as our number of clusters

```{r}
set.seed(123)
final <- kmeans(rating, 3, nstart = 25)
print(final)


movie_rating %>%
  mutate(Cluster = final$cluster) %>%
  group_by(Cluster) %>%
  summarise_all("mean")
```
Interpretation:
- Cluster 1 : cluster that gives `horror` low rate
- Cluster 3 : Cluster that gives `romcom` and `fantacy` low rate
- Cluster 2 : Cluster that gives `horror` and `action` high rate

