---
title: "Basic R Math"
author: "Aviandito, edited by Yurham Afif"
date: "4/20/2021"
output: github_document
---

## Load Packages

This is the code chunk to load `tidyverse`

```{r}
library(tidyverse)
```

## Read data

This is the code chunk to load `Indonesia.csv`

```{r}
indonesia <- read_csv('Indonesia.csv')
```

After reading data, you might want to have a quick look on the columns. You can use `glimpse()`

```{r}
glimpse(indonesia)
```

Your turn! RStudio came with a built-in dataset called `mpg`. Now please create a new code chunk to run `glimpse(mpg)`!
```{r}
glimpse(mpg)
```

## R Basics

### Declaring & putting a value into a variable

You can declare and put a value into a variable with `<-`

```{r}
a <- 5
b <- 8
```

### Basic mathematical operations

Basic mathematical expressions are similar with other languages

```{r}
addition <- a + b
substraction <- a - b
multiplication <- a * b
division <- a / b
modulo <- a %% b

paste0("Result of addition: ", addition,
      ", result of substraction: ", substraction,
      ", result of multiplication: ", multiplication,
      ", result of division: ", division,
      ", result of modulo: ", modulo)
```

### Declaring a function

You can declare a function with `function()`. Put the function argument in the brackets `()`. Enclose your code for the function with curly brackets `{}`

```{r}
a_plus_b <- function(a, b){
  a + b
}

c <- a_plus_b(a=21, b=22)

c
```

### Looping

Similar with other language, you can iterate through a list in R with `for` loop or `while` loop

For loop

```{r}
# command to declare a list
list_to_iterate <- c(12, 13, 14)

for (i in list_to_iterate){
  c <- a_plus_b(20, i)
  print(c)
}
```

While loop

```{r}
i = 1
while (i <= 3){
  c <- a_plus_b(20, list_to_iterate[i])
  print(c)
  i = i+1
}
```

### Basic wrangling & plotting in `tidyverse`

Below is a plot of % population fully vaccinated in Indonesia. Vaccination data is from Our World in Data, and 2019 population data is from The World Bank.

Your task: the code for new column `pct_fully_vaccinated` is incomplete. Please complete it with the proper calculation, which is `people_fully_vaccinated` column divided by `indo_pop_2019` variable that we declared.

```{r}
# 2019 Indonesia population from https://data.worldbank.org/indicator/SP.POP.TOTL?locations=ID
indo_pop_2019 <- 270625568

# Create a new column which shows the % of population fully vaccinated
indonesia %>%
  # TASK: Complete the code for pct_fully_vaccinated column, which is people_fully_vaccinated divided by indo_pop_2019
  mutate(pct_fully_vaccinated = people_fully_vaccinated / indo_pop_2019) %>%
  ggplot(aes(x = date, y = pct_fully_vaccinated)) +
  geom_line() +
  scale_y_continuous(labels = scales::percent) +
  labs(title = '% of population fully vaccinated, Indonesia',
       subtitle = 'People fully vaccinated are growing exponentially',
       x = 'Date',
       y = '% fully vaccinated',
       caption = 'Data source: Our World In Data, The World Bank')
```
