---
title: "Data Visualization with R"
author: "Yurham Afif"
date: "5/24/2021"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load Packages

This is the code chunk to load `tidyverse`

```{r}
library(tidyverse)
```

## Read data

This is the code chunk to load `Insurance_Loss (1).csv`

```{r}
insurance <- read.csv('Insurance_Loss (1).csv')
```

## summarise the data

see the data overview

```{r}
insurance %>% 
  summary()
insurance %>% 
  glimpse()
```

## check missing data

sum of total NA data
```{r}
insurance %>% 
  is.na() %>% 
  sum()
```

## ggplot geom_point geom_smooth `Age` x `Years.of.Driving.Experience`

this graph shows an almost linear relation between `Age` and `Years.of.Driving.Experience`. The higher age, the higher driving experience.

```{r}
ggplot(data = insurance, aes(x = Age, y = Years.of.Driving.Experience, colour = Gender)) + 
  geom_point() +
  geom_smooth()
```

## ggplot geom_point `Years.of.Driving.Experience` x `Losses` with `Gender` factor

The less driving experience, the higher losses they got, and visually dominated by male driver.

```{r}
ggplot(data = insurance, aes(x = Years.of.Driving.Experience, y = Losses)) +
  geom_point(aes(colour = Gender))
```

## ggplot geom_point `Years.of.Driving.Experience` x `Losses` with `Married` factor

Single driver make lots of losses despite of their driving experience.

```{r}
ggplot(data = insurance, aes(x = Years.of.Driving.Experience, y = Losses)) +
  geom_point(aes(colour = Married))
```

## ggplot geom_col `Fuel.Type` x `Losses`

the fuel type `D` has higher losses compared to type `P`


```{r}
ggplot(data = insurance, aes(x = Fuel.Type, y = Losses, colour = Fuel.Type)) +
  geom_col()
```


## ggplot geom_boxplot `Gender` x `Age`

this graph implies that both 'Female' and 'male' have the same distribution number of owned vehicles with median 2

```{r}
ggplot(data = insurance, aes(x = Gender, y = Age)) + 
  geom_boxplot(aes(colour = Gender))

```


