---
title: "Data Visualization with R Part 2"
author: "Adiva Shabana, edited by Yurham Afif"
date: "5/17/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Leaflet for Spacial Data Visualisation

In this chapter we want to show different US College by three different sector label: `Private`, `Public`, and `For-Profit` as a spacial data shown in interactive map.

## LEAFLET

Assign the dependence library `leaflet` and `tidyverse`

```{r}
library(leaflet)
library(tidyverse)
```

## DATASET

Open the dataset form a csv file `ipeds.csv` and see the first six data in the table

```{r}
ipeds <- read.csv('ipeds.csv')
head(ipeds)
```

## DATA CLEANSING

Remove colleges with missing sector information

```{r}
ipeds <- 
    ipeds %>% 
    drop_na()
```

## FILTER DATA

As we want to see separated college data based on its sector label, assign the filter `ipeds_for_profit`, `ipeds_public`, and `ipeds_private` for each label

```{r}
ipeds_for_profit <- ipeds %>%
        filter(sector_label == "For-Profit")
ipeds_public <- ipeds %>%
        filter(sector_label == "Public")
ipeds_private <- ipeds %>%
        filter(sector_label == "Private")
```

## VISUALISE EACH SECTOR

Assuming "lng" and "lat" column as longitude and latitude, respectively, plot each data on the map

```{r}
leaflet()  %>% 
    addProviderTiles("CartoDB")  %>% 
    addMarkers(lng = ipeds_for_profit$lng, lat = ipeds_for_profit$lat) %>%
    clearMarkers() %>%
    addCircleMarkers(lng = ipeds_for_profit$lng, lat = ipeds_for_profit$lat, radius = 2, color = "red")
```
the clickable maps showing name as popup box given below for label `ipeds_public`

```{r}
leaflet()  %>% 
    addProviderTiles("CartoDB")  %>% 
    addCircleMarkers(data = ipeds_public, radius = 2, popup = ~name, color = "blue")
```

Maps for label `ipeds_private`

```{r}
leaflet()  %>% 
    addProviderTiles("CartoDB")  %>% 
    addCircleMarkers(data = ipeds_private, radius = 2, popup = ~name, color = "green")
```